PANCHANGE_analysis

### 2020-09-07 PANCHANGE_analysis.Rmd
Minor error in new chunks fixed. Confirmed that the script runs without error.

```{r summary gender}

summarytools::freq(data_dem[(grep("gender",names(data_dem)))],
                   style = "rmarkdown")

@@

edubindat <- dat %>%
  mutate(demographics.education_binary =
           case_when(
             highest_education_numeric == "4" ~ "Bachelors or higher",
             highest_education_numeric == "3" ~ "A-levels or lower"
           )) %>%
  summarise(n = n()) %>%
  drop_na() %>%
  mutate(freq = n / sum(n))

educatdat <- dat %>%
  mutate(demographics.education_three = 
           case_when(
             highest_education_numeric == "4" ~ "Bachelors or higher",
             highest_education_numeric == "3" ~ "A-levels",
             highest_education_numeric == "1" ~ "GCSEs or lower"
           )) %>%
  summarise(n = n()) %>%
  drop_na() %>%
  mutate(freq = n / sum(n))

@@

#y = c(0.57,0.85,0.25,0.38,0.015,0.05,0.14),
#x = c(1.2,1.2,1.2,1.2,1.35,1.2,1.2)

@@

  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP sample self reported highest level of education, above or below bachelor degree or equivalent",
                      sep=" "),
        subtitle = paste("n", sum(edubindat$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.25,0.75),
                  label= paste0(round((freq*100),0),"%")),
             size=5,
             face="bold"
             )

@@

  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP sample self reported highest level of education, above or below bachelor degree or equivalent",
                      sep=" "),
        subtitle = paste("n", sum(educatdat$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.25,0.75,0.02),
                  label= c(paste0(round((freq[1:2]*100),0),"%"),"") ),
             size=5,
             face="bold"
             )

@@

```{r education pie chart - largest groups labelled }

edu_pie_somelabel <-

    edudat %>%
    mutate(demographics.highest_level_of_education = fct_reorder(demographics.highest_level_of_education,-n)) %>%

  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP sample self reported level of education",
                      sep=" "),
        subtitle = paste("n", sum(edudat$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.57,0.85,0.25,0.38,0.015,0.05,0.14),
                  x = c(1.2,1.2,1.2,1.2,1.35,1.2,1.2),
                  label=c( paste0(round((freq[1:4]*100),0),"%"),"",
                  paste0(round((freq[6:7]*100),0),"%"))),
             size=5,
             face="bold"
             )
edu_pie_somelabel

@@

edu_pie_nolabel <- 
   edudat %>%
    mutate(demographics.highest_level_of_education = fct_reorder(demographics.highest_level_of_education,-n)) %>%

  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP sample self reported level of education",
                      sep=" "),
        subtitle = paste("n", sum(edudat$n),
                         sep = " "),
        fill = "Self reported level of education")

edu_pie_nolabel

@@

```{r smart numeric summary tables}
# reshape the table
gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
  gather(key, value, -gad.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    Change = Gad.change_binary,
    SD = Sd
  )

@@

Table for knitting
gad diff summary table
```{r gad diff summary table}
kable(gad.sum_score_numeric_summary_table_reshaped)
```

@@

```{r smart numeric summary tables}
# reshape the table
gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
  gather(key, value, -gad.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
    ) %>% 
  # or we can individually rename variables 
  rename(
    Change = Gad.change_binary,
    SD = Sd
  )

@@

```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r gad percentage plot retro_prepan sum, fig.height=6, fig.width=10}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
#    labels = c("Prepandemic", "Retrospective")
    ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r smart numeric summary tables}
# reshape the table
phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>%
  gather(key, value, -phq.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

Table for knitting
phq diff summary table
```{r phq diff summary table}
kable(phq.sum_score_numeric_summary_table_reshaped)
```

@@

```{r smart numeric summary tables}
# reshape the table
phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
  gather(key, value, -phq.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r phq percentage plot retro_prepan sum, fig.height=6, fig.width=10}
dat.long.phq.sum %>%
  #  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PHQ9 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r smart numeric summary tables}
# reshape the table
ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>%
  filter(ocir.change_binary == "Worsening") %>%
  select(-ocir.change_binary) %>%
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

Table for knitting
ocir diff summary table
```{r ocir diff summary table}
kable(ocir.sum_score_numeric_summary_table_reshaped)
```

@@

```{r smart numeric summary tables}
# reshape the table
ocir.numeric_summary_table_reshaped <- ocir.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir percentage plot retro_prepan sum, fig.height=6, fig.width=10}
dat.long.ocir.sum %>%
  ggplot(mapping = aes(
    x = ocir.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "OCI-R score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r smart numeric summary tables}
# reshape the table
pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

Table for knitting
pcl diff summary table
```{r pcl diff summary table}
kable(pcl.numeric_summary_table_reshaped)
```

@@

```{r smart numeric summary tables}
# reshape the table
pcl.sum_score_numeric_summary_table_reshaped <- pcl.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r pcl percentage plot retro_prepan sum, fig.height=6, fig.width=10}
dat.long.pcl.sum %>%
  ggplot(mapping = aes(
    x = pcl.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PCL score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

Create the correlation matrix plot using the corrplot package
```{r Correlation matrix of psychiatric disorders plot, fig.height=7}
corrplot(mhd.corr.matrix, 
         method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.8,
         tl.col = "black",
         col=colorCOPINGpalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = mhd.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank" # Nonsignificant correlations have no colour
         )
```

@@

```{r RUBBISH 2 fig.height=7, fig.width=5}
gad.diff_score_base_prepan_plot /
  gad.diff_score_retro_prepan_plot /
  gad.diff_score_base_retro_plot +
  plot_layout(guides = "collect", heights = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```

>>>>

@@

edubindat <- dat %>%
  mutate(demographics.education_binary =
           case_when(
             highest_education_numeric == "4" ~ "Bachelors or higher",
             highest_education_numeric == "3" ~ "A-levels or lower",
             highest_education_numeric == "2" ~ "A-levels or lower",
             highest_education_numeric == "1" ~ "A-levels or lower"
           )) %>%
  count(demographics.education_binary) %>%
  mutate(freq = round(n/sum(n), 2)) %>% 
  drop_na()

educatdat <- dat %>%
  mutate(demographics.education_three = 
           case_when(
             highest_education_numeric == "4" ~ "Bachelors or higher",
             highest_education_numeric == "3" ~ "A-levels",
             highest_education_numeric == "1" ~ "GCSEs or lower"
           )) %>%
  count(demographics.education_three) %>%
  mutate(freq = round(n/sum(n), 2)) %>% 
  drop_na()

@@

@@

  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
                      sep=" "),
        subtitle = paste("n", sum(edubindat$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.25,0.75),
                  label= paste0(round((freq*100),0),"%")),
             size=5,
             face="bold"
             )

@@

  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
                      sep=" "),
        subtitle = paste("n", sum(educatdat$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.23,0.65,0.05),
                  label= c(paste0(round((freq[1:3]*100),0),"%")),
             size=5,
             face="bold"
             ))

@@

@@

edu_pie_nolabel <-

  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported level of education",
                      sep=" "),
        subtitle = paste("n", sum(highest_education_prop_total$n),
                         sep = " "),
        fill = "Self reported level of education")

@@

```{r gad sum score smart numeric summary tables}
# reshape the table
gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
  gather(key, value, -gad.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    Change = Gad.change_binary,
    SD = Sd
  )

@@

Table for knitting
gad sum score summary table
```{r gad sum score summary table}
kable(gad.sum_score_numeric_summary_table_reshaped)
```

@@

```{r gad diff score smart numeric summary tables}
# reshape the table
gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
  gather(key, value, -gad.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
    ) %>% 
  # or we can individually rename variables 
  rename(
    Change = Gad.change_binary,
    SD = Sd
  )

@@

```{r gad percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r gad percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
#    labels = c("Prepandemic", "Retrospective")
    ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r phq sum score smart numeric summary tables}
# reshape the table
phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>%
  gather(key, value, -phq.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

Table for knitting
phq sum score summary table
```{r phq sum score summary table}
kable(phq.sum_score_numeric_summary_table_reshaped)
```

@@

```{r phq diff score smart numeric summary tables}
# reshape the table
phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
  gather(key, value, -phq.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r phq percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r phq percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.phq.sum %>%
  #  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PHQ9 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir sum score smart numeric summary tables}
# reshape the table
ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>%
  filter(ocir.change_binary == "Worsening") %>%
  select(-ocir.change_binary) %>%
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

Table for knitting
ocir sum score summary table
```{r ocir sum score summary table}
kable(ocir.sum_score_numeric_summary_table_reshaped)
```

@@

```{r ocir diff score smart numeric summary tables}
# reshape the table
ocir.numeric_summary_table_reshaped <- ocir.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r ocir percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.ocir.sum %>%
  ggplot(mapping = aes(
    x = ocir.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "OCI-R score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r pcl sum score smart numeric summary tables}
# reshape the table
pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

Table for knitting
pcl sum score summary table
```{r pcl sum score summary table}
kable(pcl.numeric_summary_table_reshaped)
```

@@

```{r pcl diff score smart numeric summary tables}
# reshape the table
pcl.sum_score_numeric_summary_table_reshaped <- pcl.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r pcl percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.pcl.sum %>%
  ggplot(mapping = aes(
    x = pcl.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PCL score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

Create the correlation matrix plot using the corrplot package
```{r Correlation matrix of psychiatric disorders plot, fig.height=7}
corrplot(mhd.corr.matrix, 
         method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.8,
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = mhd.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank" # Nonsignificant correlations have no colour
         )
```

@@

```{r RUBBISH 2, fig.height=7, fig.width=5}
gad.diff_score_base_prepan_plot /
  gad.diff_score_retro_prepan_plot /
  gad.diff_score_base_retro_plot +
  plot_layout(guides = "collect", heights = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```
